---
title: "Data607_final"
author: "Wei Zhou"
date: "5/7/2019"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
---

Reference: http://rpubs.com/jasano/inspex
Score instruction: https://www1.nyc.gov/assets/doh/downloads/pdf/rii/how-we-score-grade.pdf
blog: https://nycdatascience.com/blog/student-works/nyc-restaurants-reviews-and-inspection-scores/


# Acquiring resturant data from NYC Open Data using API

```{r echo=FALSE}
# install.packages("RSocrata")
library(RSocrata)
library(data.table)
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidyverse)
library(httr)
library(keyring)
library(rjson)
library(yelpr)
library(RJSONIO)
library(tibble)
library(jsonlite)
```

## Read in data

###Acquire Data using NYC open data API
```{r}
 all_df<- read.socrata("https://data.cityofnewyork.us/resource/43nn-pn8j.json")
```

###It is always good to know what your data looks like. Using `Glimpse` function will give you a snapshot of your dataset. 
```{r}
glimpse(all_df)
```

## Yelp Fusion API 

#### Get Unique phone number in Open Dataset. 
```{r}
rest_phone=data.frame(all_df$camis,all_df$phone)
names(rest_phone) = c('camis','phone')
unique_rest_phone= rest_phone[!duplicated(rest_phone),]
```

#### Acquire Yelp business data.
```{r}
key <- 'yelp_api_key'
n_lower = 24947
n_upper = 27050
phone_df=unique_rest_phone[c(n_lower:n_upper),]
id = c()
rating = c()
review_count= c()
lat= c()
lon= c()
price= c()
phone_ls = c()
camis_ls = c()
for(i in 1:nrow(phone_df)) {
    row <- phone_df[i,]
    phone=paste0('+1',row$phone)
    camis=row$camis
    test=business_search_phone(api_key = key, phone_number = phone)
    camis_ls = c(camis_ls,camis)
    phone_ls = c(phone_ls,phone)
    id = c(id,test$businesses$id)
    rating=c(rating,test$businesses$rating)
    review_count = c(review_count,test$businesses$review_count)
    lat=c(lat,test$businesses$coordinates$latitude)
    lon=c(lon,test$businesses$coordinates$longitude)
    price = c(price,test$businesses$price)
}

```

#### Save yelp business data to csv. 
```{r}
business_detail= data.frame(cbind(camis_ls,phone_ls,id,rating, review_count, lat,lon,price))
csvname = paste0('./yelp_data/yelp',n_lower,'_',n_upper,'.csv')
write.csv(business_detail, file = csvname)
```

