---
title: "Data607_final"
author: "Wei Zhou, Mia Chen"
date: "5/7/2019"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
---

Reference: http://rpubs.com/jasano/inspex
Score instruction: https://www1.nyc.gov/assets/doh/downloads/pdf/rii/how-we-score-grade.pdf
blog: https://nycdatascience.com/blog/student-works/nyc-restaurants-reviews-and-inspection-scores/


# Acquiring resturant data from NYC Open Data using API

```{r echo=FALSE}
# install.packages("RSocrata")
library(RSocrata)
library(data.table)
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidyverse)
library(httr)
library(keyring)
library(rjson)
library(yelpr)
library(RJSONIO)
library(tibble)
library(jsonlite)
```

## Read in data

###Acquire Data using NYC open data API
```{r}
 all_df<- read.socrata("https://data.cityofnewyork.us/resource/43nn-pn8j.json")
```

###It is always good to know what your data looks like. Using `Glimpse` function will give you a snapshot of your dataset. 
```{r}
glimpse(all_df)
```

### Tidy up data

#### Convert date information to date class
```{r}
all_df$grade_date <- as.Date(all_df$grade_date, "%Y-%m-%d")
all_df$inspection_date <- as.Date(all_df$inspection_date, "%Y-%m-%d")
all_df$record_date <- as.Date(all_df$record_date, "%Y-%m-%d %h:%m:%s")
```

## Yelp Fusion API 

#### Get Unique phone number in Open Dataset. 
```{r}
rest_phone=data.frame(all_df$camis,all_df$phone)
names(rest_phone) = c('camis','phone')
unique_rest_phone= rest_phone[!duplicated(rest_phone),]
```

#### Acquire Yelp business data.
```{r}
key <- 'yelp_api_key'
n_lower = 24947
n_upper = 27050
phone_df=unique_rest_phone[c(n_lower:n_upper),]
id = c()
rating = c()
review_count= c()
lat= c()
lon= c()
price= c()
phone_ls = c()
camis_ls = c()
for(i in 1:nrow(phone_df)) {
    row <- phone_df[i,]
    phone=paste0('+1',row$phone)
    camis=row$camis
    test=business_search_phone(api_key = key, phone_number = phone)
    camis_ls = c(camis_ls,camis)
    phone_ls = c(phone_ls,phone)
    id = c(id,test$businesses$id)
    rating=c(rating,test$businesses$rating)
    review_count = c(review_count,test$businesses$review_count)
    lat=c(lat,test$businesses$coordinates$latitude)
    lon=c(lon,test$businesses$coordinates$longitude)
    price = c(price,test$businesses$price)
}

```

#### Save yelp business data to csv. 
```{r}
business_detail= data.frame(cbind(camis_ls,phone_ls,id,rating, review_count, lat,lon,price))
csvname = paste0('./yelp_data/yelp',n_lower,'_',n_upper,'.csv')
write.csv(business_detail, file = csvname)
```

There were 27050 rows of data and we could only retrieve 5000 at a time, thus we had 6 csv files to contain all the data. These 6 csv files were uploaded to Github.

#### Read csv files from github
```{r}
yelp1 <- read.csv("https://raw.githubusercontent.com/weizhou2273/data607_final/master/yelp_data/yelp1_5000.csv")
yelp2 <- read.csv("https://raw.githubusercontent.com/weizhou2273/data607_final/master/yelp_data/yelp5001_10000.csv")
yelp3 <- read.csv("https://raw.githubusercontent.com/weizhou2273/data607_final/master/yelp_data/yelp10001_15000.csv")
yelp4 <- read.csv("https://raw.githubusercontent.com/weizhou2273/data607_final/master/yelp_data/yelp15001_19946.csv")
yelp5 <- read.csv("https://raw.githubusercontent.com/weizhou2273/data607_final/master/yelp_data/yelp19947_24946.csv")
yelp6 <- read.csv("https://raw.githubusercontent.com/weizhou2273/data607_final/master/yelp_data/yelp24947_27050.csv")
```

#### Combine all yelp dataframes as a single dataframe
```{r}
yelp_df <- as.data.frame(rbind(yelp1, yelp2, yelp3, yelp4, yelp5, yelp6))
```

```{r}
glimpse(yelp_df)
```


```{r}
yelp_df$phone_ls <- as.character(yelp_df$phone_ls)
yelp_df$phone_ls <- str_replace_all(yelp_df$phone_ls, "^\\+1", "")
```

```{r}
yelp_df <- yelp_df %>% rename(phone = phone_ls)
```


### Merge data from two sources into one dataframe

```{r}
restaurant <- merge(all_df, yelp_df, by = "phone")
```

```{r}
glimpse(restaurant)
